Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-07-30 190410_Paper_ACPR/combined1.tex
acpr2019: submit

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{subfigure}

@@

\subsection{Triplet Network}
% triplet network
Triplet network is a kind of metric learning model~\cite{} which aims to learn useful representations by distance comparisons~\cite{hoffer2015deep}. It is widely used in person re-identification, which solves the matching problem of individuals and identity between camera images~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. 
Distinction between classes may be ambiguous in this task as the similarity features between an individual is relatively small compare to the background features such as pose, hair and textures.

% training triplet network
To address this problem, the training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive (similar) data more closer to the anchor (reference) and the negative (dissimilar) data to keep away from the anchor. Triplet network receives above triplet data as an input, which is the anchor (reference), positive (similar) and negative (dissimilar) data.

% optimize training
Since myriad triplet pairs can be generated in the training set, training with all possible triplets may time-consuming and unnecessary. Optimizing training becomes necessary by mining the efficient triplet pairs out of all possible pairs.
\cite{cheng2016person,ding2015deep,wang2016joint} generates triplet only for small classes, which randomly selected in each iteration.
Recently, \cite{schroff2015facenet} used triplet mining strategy for faster convergence speed. They selects inputs from large mini-batch at each training iteration using the network during training.
However, a lot of training data is necessary to make such a large-sized mini-batch.

@@

Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$. $\mathbf{W}_{i}$ can be obtained as follows:

\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
\end{equation}

@@

\begin{figure}[!h]
   \begin{center}
   \subfigure[][Analysis on image brightness changes]{
        \includegraphics[height=6.2cm]{fig_roc_v9.eps}}
   \subfigure[][Analysis on image contrast changes]{
        \includegraphics[height=6.2cm]{normalized_loss_curve_ma30_v1.eps}}
   \caption{Robustness of the images varying amount of
        brightness and contrast at pixel level. Graph labeled as (a)
        shows the Euclidean distance between Fig.~\ref{shifttern}
        (b) and Fig.~\ref{shifttern} (a), and graph (b) shows the
        Euclidean distance between Fig.~\ref{shifttern} (c) and
        Fig.~\ref{shifttern} (a).}
   \label{shifttern2}
   \end{center}
\end{figure}

\iffalse
% Figure 3
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{fig_roc_v5.eps}
    \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
\end{figure}

% Figure 2
    \begin{figure}[!h]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
    \caption{Training Loss Curve of the Proposed System} \label{fig2}
\end{figure}
\fi

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}

@@

\subsection{Triplet Network}
% metric learning
Metric learning is the training of models to learn a distance function to find similarities between objects. 
% triplet network
Triplet network a metric learning model which aims to learn useful representations by distance comparisons \cite{hoffer2015deep}. It is widely used in face recognition \cite{schroff2015facenet} and person re-identification, which solves the matching problem of individuals and identity between camera images\cite{cheng2016person,chen2017beyond}. In above tasks, distinction between classes may be ambiguous as the textures or features of the targets may be similar looking.

% training triplet network
Triplet network receives triplet data pairs as input. Triplet is composed of anchor(reference), positive(similar) and negative(dissimilar) data.
The training of the triplet network is making feature vectors to be placed in the appropriate separation space, making the positive(similar) data is close to the anchor(reference) and the negative(dissimilar) data is kept away from the anchor.

% optimize training
Since myriad triplet pairs may exist for the training set, training from all possible pairs may time-consuming and unnecessary. Optimizing training becomes necessary as it mines the learning-efficient triplet out of large possible inputs.
There are many ways to optimize training. In \cite{schroff2015facenet}, selects inputs from large mini-batch at each training iteration using the network during training. \cite{cheng2016person} adds second margin for triplet loss to expand intra-class distance.
Following in \cite{chen2017beyond}, quadruplet loss function makes the distance between the same classes is less than the distance between any different classes.

@@

% training KARnet
Network learning is archived using one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$.
After that, we have the weight matrix $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ to train. the weight matrix can be separated into weights and bias term as
$\mathbf{W}_{2}\dots\mathbf{W}_{i}$ = 
$\begin{bmatrix}
\mathbf{w}_{2}^{T}\\\mathnormal{W}_{2}
\end{bmatrix}
\dots
\begin{bmatrix}
\mathbf{w}_{i}^{T}\\\mathnormal{W}_{i}
\end{bmatrix}$.

after assign random weights to $\mathbf{W}_{1}\dots\mathbf{W}_{i}$ , we get $\mathbf{W}_{1}$. it is solved as follows:

\begin{equation*}
    \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger = 
    \sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)
\end{equation*}
\begin{equation*}
    \begin{aligned}
        \Rightarrow
        \biggl[\sigma^{-1}\biggl(
        \dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger} 
        = \sigma\left(\mathbf{X}\mathbf{W}_{1}\right)
    \end{aligned}
\end{equation*}
\begin{equation}
    \begin{aligned}
        \Rightarrow
        \mathbf{X}^{\dagger}\sigma^{-1}\biggl(
        \biggl[\sigma^{-1}\biggl(
        \dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        - \mathbf{1}\cdot\mathbf{w}_{2}^{T}\biggr]\mathnormal{W}_{2}^{\dagger}
        = \mathbf{W}_{1} .
    \end{aligned}
\end{equation}

After deriving the $\mathbf{W}_{1}$, the $\mathbf{W}_{2}$ also can be optimized as:

%\begin{multline*}
\begin{equation}
    \begin{aligned}
        \Rightarrow
        \left(\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right)^{\dagger}
        \biggl(\dots
        \biggl[\sigma^{-1}\biggl(
            \left[\sigma^{-1}\left(\mathbf{Y}\right)-\mathbf{1}\cdot\mathbf{w}_{i}^{T}\right]\mathnormal{W}_{i}^\dagger
        \biggr)
        - \mathbf{1}\cdot\mathbf{w}_{(i-1)}^{T}\biggr]\mathnormal{W}_{(i-1)}^{\dagger}
        \dots\biggr)\\
        = \mathbf{W}_{2} .
    \end{aligned}
\end{equation}
%\end{multline*}

By repeating this process recursively until all weight matrix values are obtained, the $\mathbf{W}_{i}$ can be obtained as follows:
\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
\end{equation}

@@

% Figure 3
\begin{figure}[!h]
    \includegraphics[width=\textwidth]{fig_roc_v5.eps}
    \caption{Receiver Operating Characteristic(ROC) Curve of the Proposed System} \label{fig3}
\end{figure}

% Figure 2
    \begin{figure}[!h]
    \includegraphics[width=\textwidth]{normalized_loss_curve_ma30_v1.eps}
    \caption{Training Loss Curve of the Proposed System} \label{fig2}
\end{figure}
